---
title: "p8105_hw5_js5431"
author: "J Shearston"
date: "November 5, 2018"
output: github_document
---

```{r setup, include=FALSE}

library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))

```

## Problem 1

### Read in and tidy data

```{r p1 file name and path vars}

file_names = list.files("./data")

paths = tibble(file_names) %>% 
  mutate(file_names = str_c("./data/", file_names))

```


```{r p1 functions}

## read in files
readin = function(x) {
  read_csv(file = x)
}

## tidy observation data
obs_cleanup = function(x){
  gather(x, key = week, value = obs_data, week_1:week_8) %>% 
    mutate(week = str_replace(week, "week_", ""))
}


```


```{r p1 read in and clean, message=FALSE}

study_data = 
  paths %>% 
  mutate(data = map(file_names, readin),
         id = str_replace(file_names, "./data/", ""),
         id = str_replace(id, ".csv", ""),
         exp_group = str_detect(id, "exp"),
         data = map(data, obs_cleanup)) %>% 
  select(-file_names)

```

### Spaghetti plot

Figure 1 depicts spaghetti plots for each research subject over time, faceted by study arm. The control group (FALSE facet) has markedly lower observation values over time when compared to the experimental group (TRUE facet). While the control group's numbers remain fairly stable and even slightly decline after eight weeks, with some variation, the experimental group's numbers clearly increase over the eight week period. 

```{r p1 spaghetti plot}

study_data %>% 
  unnest() %>%
  mutate(week = as.numeric(week)) %>% 
  ggplot(aes(x = week, y = obs_data, color = id)) +
  geom_line() +
  facet_grid(~exp_group) +
  labs(
    title = "Figure 1. Observation Value over Time, by Subject",
    x = "Week",
    y = "Observation Value",
    caption = "Control Group = FALSE, Experimental Group = TRUE") +
  theme(legend.position="none")
  
```


## Problem 2


```{r p2 import data}

hom_data = read_csv("homicide-data.csv")

```

### Washington Post Homicide Data

The Washington Post homicide data contains information on homicides from 50 major US cities, from the years 2007 to 2015. The dataset contains `r nrow(hom_data)` rows and `r ncol(hom_data)` columns. Variables include a unique identifer for each homicide, homicide related variables including the reported date of the homicide and the case dispsition, information about the vicitim, including the victim's first and last name, age, sex, and race, and geographic location, including the city, state, latitude, and longitude of the homicide. 

### Total number of homicides and unsolved homicides by city

```{r p2 city num homs & unsolv}

hom_data = hom_data %>%
  mutate(city_state = str_c(city, ", ", state))

unsolved = hom_data %>% 
  group_by(city_state) %>% 
  mutate(unsolv_true = str_detect(disposition, "without|No")) %>% 
  summarise(num_homs = n_distinct(uid),
            num_unsolv_homs = sum(unsolv_true == "TRUE"))

knitr::kable(unsolved)

```

### Baltimore, MD

```{r}

results_pt_bmd <- prop.test(x = unsolved$num_unsolv_homs[[3]], n = unsolved$num_homs[[3]])

broom::tidy(results_pt_bmd)

  
```

